---
title: "LA 1"
author: "Pooja(1NT18IS110) , Pranathi(1NT18IS113)"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## LA1 ASSIGNMENT
#### Dataset :Pokemon and their stats

### Description of Data

This data set includes 1045 Pokemons, including their number, name, and basic stats: HP, Attack, Defense, Special Attack, Special Defense, and Speed. It has been of great use when teaching statistics to kids. With certain types you can also give a geeky introduction to machine learning.


Name: Name of each pokemon.
Total: sum of all stats that come after this, a general guide to how strong a pokemon is.
HP: hit points, or health, defines how much damage a pokemon can withstand before fainting.
Attack: the base modifier for normal attacks (eg. Scratch, Punch).
Defense: the base damage resistance against normal attacks.
SP Atk: special attack, the base modifier for special attacks (e.g. fire blast, bubble beam).
SP Def: the base damage resistance against special attacks.
Speed: determines which pokemon attacks first each round.
```{r}
pokemon_data=read.csv(file=file.choose(),header = TRUE)
```
Display head of data
```{r}
head(pokemon_data)
```
Display first n rows specified.
```{r}
head(pokemon_data,n=10)
```
It displays first 10 rows.


Display tail of data.
```{r}
tail(pokemon_data)
```
Display n rows specified from bottom
```{r}
tail(pokemon_data,n=10)
```
It displays last 10 rows.

Determining Type of data
```{r}
class(pokemon_data)
```
Determine structure of data
```{r}
str(pokemon_data)
```
Summarising the data 
```{r}
summary(pokemon_data)
```
for Numerical data coloumns like Total,HP,Summary command shows the Minimum value, Maximum value, Mean, Meadian, 1st and 3rd quartiles.
For Text data coloumns summary command will give the total number of records of that coloumn and class of that coloumn.

Displaying Dimension of the data
```{r}
dim(pokemon_data)
```
The dataset contains 1045 rows and 8 coloumns.

Displaying coloumn names of data
```{r}
colnames(pokemon_data)
```
Displaying structure of some coloumns in the data
```{r}
class(pokemon_data$Name)
```
```{r}
class(pokemon_data$Total)
```
Displaying type of some data structure in the data
```{r}
typeof(pokemon_data$Name)
```
```{r}
typeof(pokemon_data$Total)
```
List of variables present in pokemon data
```{r}
ls(pokemon_data)
```
Some pattern matching operations on variable of pokemon_data
```{r}
ls(pokemon_data,pattern="^Sp")
```
variables which starts with letters SP

```{r}
ls(pokemon_data,pattern="^[AD]")
```
Variables whose name starts with A or D

```{r}
ls(pokemon_data,pattern="t.l")
```
Variables starts with t and ending l.

```{r}
ls(pokemon_data,pattern="ce$")
```
Variables names ending with pattern ce.
